Dependent Object Types

### 2012-09-21 doc/fool/article.tex
wip
a bit more of the expansion derivation

The expansion judgement $\Gamma \ts T \expand_z {\seq {D}}$
``flattens'' all the declarations of a type: it relates a type $T$ to
a set of declarations that describe the type structurally. Expansion
is precise and unique, though it doesn't always
exist.

@@

\subsection{Glbs and Lubs}

@@

We represent it as follows in DOT:
\begin{align*}
\mlnew p {&\Top \mlrefine p {\\
&\ \Ldecl {A_c} \Bot {\Top \refine z {\Ldecl T \Bot {z.A_c}}}\\
&\ \Ldecl {B_c} \Bot {\Top \refine z {\Ldecl T \Bot {z.B_c}}}\\
&}\ldefs{}}{}
\end{align*}

@@

What is the expansion of $p.A_c \tand p.B_c$? It is the set ${\Ldecl T
  \Bot {p.A_c \tand p.B_c}}$.

>>>>

The expansion judgement $\Gamma \ts T \expand_z {\seq {D}}$
``flattens'' all the declarations of a type: it relates a type $T$ to
a set of declarations that describe the type structurally. Expansion
is precise and unique, though it doesn't always exist. See
section~\ref{ex-exp} for examples.

@@

\subsection{Glbs and Lubs}\label{ex-exp}

@@

We represent it as follows in DOT, wrapping the types in a namespace $p$:
\begin{align*}
\mlnew p {&\Top \mlrefine p {\\
&\ \Ldecl {A_c} \Bot {\Top \refine z {\Ldecl T \Bot {p.A_c}}}\\
&\ \Ldecl {B_c} \Bot {\Top \refine z {\Ldecl T \Bot {p.B_c}}}\\
&}\ldefs{}}{}
\end{align*}

@@

The expansion of $p.A_c \tand p.B_c$ is the set $\{\Ldecl T \Bot
{p.A_c \tand p.B_c}\}$ by \textsc{$\tand$-$\expand$} rule:

\

{\tiny
\prooftree
     p.A_c \expand_z \{\Ldecl T \Bot {p.A_c}\}\quad
     p.B_c \expand_z \{\Ldecl T \Bot {p.B_c}\}
\justifies
     p.A_c \tand p.B_c \expand_z \{\Ldecl T \Bot {p.A_c \tand p.B_c}\}
\using
     \textsc{$\tand$-$\expand$}
\endprooftree
}

\

In turn, $p.A_c \expand_z \{\Ldecl T \Bot {p.A_c}\}$ is derived as
follows:

\

{\tiny
\prooftree
   \[
   \ldots
   \justifies
   p \ni {\Ldecl {A_c} \Bot {\Top \refine z {\Ldecl T \Bot {p.A_c}}}}\quad
   \using
   \textsc{path-$\ni$}
   \]
   \[
   \[
   \justifies
   \Top \expand_z \{\}
   \using
   \textsc{$\Top$-$\expand$}
   \]
   \justifies
   {\Top \refine z {\Ldecl T \Bot {p.A_c}}} \expand_z \{\Ldecl T \Bot {p.A_c}\}
   \using
   \textsc{rfn-$\expand$}
   \]
\justifies
   p.A_c \expand_z \{\Ldecl T \Bot {p.A_c}\}
\using
     \textsc{tsel-$\expand$}
\endprooftree
}
